### 2022-02-14 README.Rmd
README added & testthat added (empty curretly)

# melt

<!-- badges: start -->
[![R-CMD-check](https://github.com/markean/melt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/markean/melt/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/melt)](https://CRAN.R-project.org/package=melt)
<!-- badges: end -->

The goal of melt is to ...

## Installation

You can install the development version of melt from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("markean/melt")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(melt)
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

>>>>

# melt - Multiple Empirical Likelihood Tests
<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/melt)](https://CRAN.R-project.org/package=melt)
[![R-CMD-check](https://github.com/markean/melt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/markean/melt/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Overview
The R package **melt** provides a unified framework for data analysis with empirical likelihood methods. A collection of functions are available for basic regression analysis and hypothesis testing. Much of its functionality and syntax are designed to mimic the corresponding base R functions. The core routines are written in C++ and utilize OpenMP for parallelization.

## Installation
You can install the latest stable release from [CRAN](https://cran.r-project.org/package=melt).
```{r eval = FALSE}
install.packages("melt", dependencies = TRUE)
```
You can install the latest development version from
[Github](https://github.com/markean/melt).
```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("markean/melt")
```

## Usage
```{r eval = FALSE}
library(melt)
# one sample test (mean)
el_mean(par = 0, x = rnorm(n = 100))

# linear regression
fit <- el_lm(formula = mpg ~ wt, data = mtcars)
summary(fit)

# analysis of variance
el_aov(formula = Sepal.Length ~ Species, data = iris)
```
